**The status of the microbial census: an update**

### 2016-02-03 Schloss_Census2_mBio_2016.Rmd
Put supplemental table captions into paper

>>>>

**Supplemental Table 1. Description of environmental categories and the criteria used to assign sequences to each category.**

**Supplementary Table 2. Frequency that each bacterial phylum was sequenced before and after 2006.**

**Supplementary Table 3. Frequency that each archaeal phylum was sequenced before and after 2006.**

**Supplementary Table 4. Frequency that each bacterial phylum was found across each of the environmental categories.**

**Supplementary Table 5. Frequency that each archaeal phylum was found across each of the environmental categories.**

**Supplementary Table 6. Frequency that each bacterial sequence or OTU was retrieved by cultivation or by culture-independent methods.**

**Supplementary Table 7. Frequency that each archaeal sequence or OTU was retrieved by cultivation or by culture-independent methods.**
